### 2021-11-19 papers/main.tex
Friday commit

\section{Introduction}
Bayesian reinforcement learning is an approach to RL that expresses uncertainty in the
Markov decision process (MDP) via a posterior distribution \citep{ghavamzadeh_bayesian_2015}.
The posterior captures the uncertainty in transition and reward distributions.

\section{Background}
\citet{fellows_bayesian_2021} defines the Bayesian Bellman operator (BBO) as:
\begin{equation}
    \B_{\omega, N}^\star(s,a) \defeq \E_{P(\phi \vert \D_\omega^N)} \left[ \hat{B}_\phi(s,a) \right],
\end{equation}
where \(\hat{B}_\phi(s,a) = \E_{P(b \mid s, a, \phi)}[b]\), is the conditional mean of the
parametric distribution \(P(b \vert s, a, \phi)\), which is a model of the true
data-generating distribution \(P(b \vert s, a, \omega)\). They further show that we can
find \(\omega^\star\) such that \(\hat{Q}_{\omega^\star} = \B^\star_{\omega^\star, N}\)
by minimising the mean squared Bayesian Bellman error (MSBBE):

\begin{equation}
    \mathrm{MSBBE}_N(\omega) \defeq \lVert \hat{Q}_{\omega} - \B^\star_{\omega, N} \lVert^2_{\rho, \pi}
\end{equation}
An unbiased estimate of \(\nabla_\omega \mathrm{MSBBE}_N(\omega)\) can be calculated as
long as we can sample from \(P(\phi \vert \D_\omega^N)\).

@@

@@

\begin{equation}
    M = \{(s_i, a_j) \; \forall s_i \in \D_\omega^N,\, \forall a_j \in \action\}. 
\end{equation}
To justify this we need to show that \(supp(c) = \state \times \action\). Assumption 1 from
\citet{fellows_bayesian_2021} assumes that each state \(s_i\) is drawn i.i.d from a distribution with
support over \(\state\), or from an ergodic Markov chain defined over a \(\sigma\)-algebra that is
countably generated from \(\state\). If we keep this assumption, then by definition \(supp(c) = \state \times \action\).

@@

\begin{algorithm}
\caption{Functional Bayesian RL}
\begin{algorithmic}
    \State \(\D \gets \emptyset\)
    \State \(s \sim P_0\)
    \State Initialize \(\phi, \omega\)
    \While{not converged}
        \State \(f \sim q_\phi\)
        \State \(a \sim \arg\max_a f(s,a)\)
        \State \(s' \sim P(\cdot \vert s,a)\)
        \State \(r = r(s',a,s)\)
        \State \(\D \gets \D \cup \{s,a,r,s'\}\)
        \State \Call{UpdatePosterior}{$\phi, \omega, \D$}
    \EndWhile
    \Statex
    \Function{UpdatePosterior}{$\phi, \omega, \D$}
    \State \(k \gets 0\)
        \While{not converged}
            \State \(T \sim \D\)
            \State \(\f \gets \{f_i \sim q_\phi \text{ for } i=1,\dots,k\}\)
            \State \(\mathcal{F} \gets \emptyset\)
            \State \(\Delta_\mathcal{L} \gets 0\)
            \For{\(\{s,a,r,s'\} \in T\)}
                \State \(\bm{\hat{a}} \gets \arg\max_a \f(s,a)\)
                \State \(\mathcal{F} \gets \mathcal{F} \cup \f(s,a)\)
                \State \(G \gets r + \gamma Q_\omega(s,a)\)
                \State \(\Delta_\mathcal{L} \gets \Delta_\mathcal{L} - \frac{1}{k} \frac{1}{\lvert T \rvert} \nabla_\phi \log p(\bm{\hat{a}} \vert G)\)
            \EndFor
            \State \(\Delta_\KL \gets SSGE(p, \mathcal{F})\)
            \State \(\phi \gets \phi + \eta_\phi (\Delta_\mathcal{L} - \Delta_\KL)\)
            \State \(\hat{B}_\phi \gets \frac{1}{k}\frac{1}{\lvert T \rvert}\sum_{i=1}^k \sum_{b \in \mathcal{F}} b\)
            \State \(\Delta_\omega \gets \sum_{\{s,a,r,s'\} \in T} \nabla_\omega \lVert \hat{B}_\phi(s,a) - Q_\omega(s,a) \rVert^2_2 \)
            \State \(\omega \gets \omega - \eta_\omega \Delta_\omega\)
        \EndWhile
    \EndFunction
\end{algorithmic}
\end{algorithm}

\section{Background}
A reinforcement learning environement is modelled as a Markov decision process (MDP)
\(M = \langle \state, \action, R, P, P_0, \gamma \rangle\), where \(\state\) is the
state space and \(\action\) is the set of available actions. At time \(t=0\) a state
\(s_0\) is sampled from the distribution \(P_0(\cdot)\). At each timestep an action
\(a_t \sim \pi(\cdot \vert s_t)\) is selected and the agent transitions to a new state
state \(s_{t+1} \sim P(\cdot \vert s_t, a_t)\). A scalar reward
\(r_t \sim R(\cdot \vert s_{t+1}, s_t, a_t)\) is observed.

>>>>

% \section{Introduction}
% Bayesian reinforcement learning is an approach to RL that expresses uncertainty in the
% Markov decision process (MDP) via a posterior distribution \citep{ghavamzadeh_bayesian_2015}.
% The posterior captures the uncertainty in transition and reward distributions.

\section{Background}
A reinforcement learning environement is modelled as a Markov decision process (MDP)
\(M = \langle \state, \action, r, P, P_0, \gamma \rangle\), where \(\state\) is the
state space and \(\action\) is the set of available actions. At time \(t=0\) a state
\(s_0\) is sampled from the distribution \(P_0(\cdot)\). At each timestep an action
\(a_t \sim \pi(\cdot \vert s_t)\) is selected and the agent transitions to a new state
state \(s_{t+1} \sim P(\cdot \vert s_t, a_t)\). A scalar reward
\(r_{t+1} = r(\cdot \vert s_{t+1}, s_t, a_t)\) is observed. As the agent and environement
interact in a sequence of time steps, a history of observations
\(\mathcal{H}_t = (s_0, a_0, s_1, r_1, a_1, s_2, r_2, \dots, s_t, r_t)\) is collected.
The goal is to find a policy \(\pi^\star\), such that sampling actions
\(a \sim \pi^*(\cdot \vert s)\) maximizes the expected future reward,
\(J^\pi \defeq \E_\pi \left[ \sum_{t=0}^\infty \gamma^t r_t \right]\). An efficient
agent must be able to learn from the data it collects, but since the data is
dependent on the policy, it must also prioritize to explore states and actions that
the agent can learn a lot from.

The \(Q\)-function, \(Q^\pi(s,a)\), is defined as the expected reward of taking action
\(a\) in state \(s\) and then following policy \(\pi\) thereafter:
\(Q^\pi \defeq \E_\pi \left[ \sum_{t=0}^\infty \gamma^t r_t \vert s_0=0, a_0=0 \right]\).
The Bellman operator on \(Q^\pi\) is defined as
\(\B[Q^\pi](s_t,a_t) \defeq \E_{P(s_{t+1} \vert s_t, a_t)\pi(a_{t+1} \vert s+t)}
\left[ r(s_{t+1}, s_t, a) + \gamma Q^\pi(s_{t+1}, a_{t+1}) \right]\). With the
\(Q\)-function we can define a policy \(\pi(a \vert s) = \arg\max_a Q(s,a)\).
In deep RL, we model \(Q\) with a neural network \(\hat{Q}_\omega\).
One way to facilitate exploration in this policy is to introduce uncertainty in the
\(Q\)-value. \cite{fellows_bayesian_2021} does this by defining the Bayesian Bellman
operator (BBO). They define \(P_B(b \vert s, a, \omega)\) as the distribution over
Bellman functions such that for a noisy sample \(b_i \sim P_B(b \vert s,a,\omega)\),
\(b_i = \B[\hat{Q}_\omega](s_i, a_i) + \eta_i\). Then we approximate this with a
distribution parameterized by \(\phi\) such that
\(P(b \vert s,a,\phi) \approx P(b \vert s,a,\omega)\).
\begin{equation}
    \B_{\omega, N}^\star(s,a) \defeq \E_{P(\phi \vert \D_\omega^N)} \left[ \hat{B}_\phi(s,a) \right].
\end{equation}
Here, \(\hat{B}_\phi(s,a) = \E_{P(b \mid s, a, \phi)}[b]\), is the conditional mean of
\(P(b \vert s, a, \phi)\), and the data \(\D_\omega^N\) is defined as the collection of
sampled \(Q\)-values, states and actions \(\D_\omega^N \defeq \{b_i, s_i, a_i\}_{i=1:N}\).
Under the assumption that each state \(s_i\) is drawn i.i.d from a distribution with
support over \(\state\), or from an ergodic Markov chain defined over a \(\sigma\)-algebra that is
countably generated from \(\state\) they find that \(\omega^\star\) such that
\(\hat{Q}_{\omega^\star} = \B^\star_{\omega^\star, N}\) can be found 
by minimising the mean squared Bayesian Bellman error (MSBBE):
\begin{equation}
    \mathrm{MSBBE}_N(\omega) \defeq \lVert \hat{Q}_{\omega} - \B^\star_{\omega, N} \lVert^2_{\rho, \pi},
\end{equation}
And that an unbiased estimate of \(\nabla_\omega \mathrm{MSBBE}_N(\omega)\) can be calculated
as long as we can sample from \(P(\phi \vert \D_\omega^N)\).

@@

% \section{Background}
% \citet{fellows_bayesian_2021} defines the Bayesian Bellman operator (BBO) as:
% \begin{equation}
%     \B_{\omega, N}^\star(s,a) \defeq \E_{P(\phi \vert \D_\omega^N)} \left[ \hat{B}_\phi(s,a) \right],
% \end{equation}
% where \(\hat{B}_\phi(s,a) = \E_{P(b \mid s, a, \phi)}[b]\), is the conditional mean of the
% parametric distribution \(P(b \vert s, a, \phi)\), which is a model of the true
% data-generating distribution \(P(b \vert s, a, \omega)\). They further show that we can
% find \(\omega^\star\) such that \(\hat{Q}_{\omega^\star} = \B^\star_{\omega^\star, N}\)
% by minimising the mean squared Bayesian Bellman error (MSBBE):

% \begin{equation}
%     \mathrm{MSBBE}_N(\omega) \defeq \lVert \hat{Q}_{\omega} - \B^\star_{\omega, N} \lVert^2_{\rho, \pi}
% \end{equation}
% An unbiased estimate of \(\nabla_\omega \mathrm{MSBBE}_N(\omega)\) can be calculated as
% long as we can sample from \(P(\phi \vert \D_\omega^N)\).

% Nonlinear function approximators such as neural networks typically have an intractable
% posterior, so we cannot calculate the posterior analytically. Instead we use a posterior approximation
% \(q(\phi \vert \D_\omega^N) \approx P(\phi \vert \D_\omega^N)\), together with an algorithm
% for approximate inference. \citet{fellows_bayesian_2021} presents the Bayesian Bellman Actor-Critic
% using randomized priors \citep{osband_randomized_2018}, and show state of the art exploratory
% behaviour.

% For most approximate inference methods in deep learning, it is difficult to incorporate domain
% knowledge into the prior. Typically the prior distribution is defined on the parameters as \(P(\phi)\),
% while the knowledge exists in the function space \(P(a \vert s)\).

% Functional variational Bayesian neural networks \citep{sun_functional_2019} lets us define a prior on the
% \emph{function space}. In a Q-learning algorithm, this would be a function
% \(f : \state \times \action \rightarrow \R\). For now we generalize, and say that
% \(f : \mathcal{X} \rightarrow \mathcal{Y}\).
% \citet{sun_functional_2019} show that for two stochastic processes \(P\) and \(Q\):

% \begin{equation}
%     \KL[P \Vert Q] = \sup_{n \in \N, \X \in \mathcal{X}^n} \KL \left[ P_\X \Vert Q_\X \right],
% \end{equation}

% where \(\X \in \mathcal{X}^n\) is a finite measurement set and \(P_\X, Q_\X\) are the marginal distributions
% at \(\X\). They further show that if \(\f^\X\) are the function values at points \(\X\), then

% \begin{multline}\label{eq:fkl}
%     \nabla_\phi \KL[q_\phi(\f^X) \Vert p(\f^\X)] \\
%     = \E \left[ \nabla_\phi \f^\X( \nabla_\f \log q(\f^\X) - \nabla_\f \log p(\f^\X)) \right].
% \end{multline}

% The difficult part in \eqref{eq:fkl} is to estimate \(\nabla_\f \log q(\f^\X)\) and \(\nabla_\f \log p(\f^\X)\).
% To estimate these log-density gradients, they use a spectral Stein gradient estimator \citep{shi_spectral_2018}.
% Given enough function value samples, the spectral Stein gradient estimator can estimate score functions
% for both in-distribution and out-of-distribution samples. This means that we can use it to estimate
% both gradients. \(\nabla_\f \log q(\f^\X)\) is likely intractable intractable, considering \(q_\phi\) is
% a neural network with stochastic weights. Depending on how we define the prior, however, \(\nabla_\f \log p(\f^\X)\)
% can be easy to compute analytically. To reduce variance in the gradients we aim to define tractable priors.

@@

\begin{equation}
    M = \{(s_i, a_j) \; \forall s_i \in \D_\omega^N,\, \forall a_j \in \action\}. 
\end{equation}
To justify this we need to show that \(supp(c) = \state \times \action\).
Under the same assumption about the distribution of each state \(s_i\) from BBO,
\(supp(c) = \state \times \action\) follows trivially.

@@

\begin{algorithm}
\caption{Functional Bayesian RL}
\begin{algorithmic}
    \State \(\D \gets \emptyset\)
    \State \(s \sim P_0\)
    \State Initialize \(\phi, \omega\)
    \While{not converged}
        \State \(f \sim q_\phi\)
        \State \(a \sim \arg\max_a f(s,a)\)
        \State \(s' \sim P(\cdot \vert s,a)\)
        \State \(r = r(s',a,s)\)
        \State \(\D \gets \D \cup \{s,a,r,s'\}\)
        \State \Call{UpdatePosterior}{$\phi, \omega, \D$}
    \EndWhile
    \Statex
    \Function{UpdatePosterior}{$\phi, \omega, \D$}
        \While{not converged}
            \State \(T \sim \D\)
            \State \(\f \gets \{f_i \sim q_\phi \text{ for } i=1,\dots,k\}\)
            \State \(\mathcal{F} \gets \emptyset\)
            \State \(\Delta_\mathcal{L} \gets 0\)
            \For{\(\{s,a,r,s'\} \in T\)}
                \State \(\bm{\hat{a}} \gets \arg\max_a \f(s,a)\)
                \State \(\mathcal{F} \gets \mathcal{F} \cup \f(s,a)\)
                \State \(G \gets r + \gamma Q_\omega(s,a)\)
                \State \(\Delta_\mathcal{L} \gets \Delta_\mathcal{L} - \frac{1}{k} \frac{1}{\lvert T \rvert} \nabla_\phi \log p(\bm{\hat{a}} \vert G)\)
            \EndFor
            \State \(\Delta_\KL \gets SSGE(p, \mathcal{F})\)
            \State \(\phi \gets \phi + \eta_\phi (\Delta_\mathcal{L} - \Delta_\KL)\)
            \State \(\hat{B}_\phi \gets \frac{1}{k}\frac{1}{\lvert T \rvert}\sum_{i=1}^k \sum_{b \in \mathcal{F}} b\)
            \State \(\Delta_\omega \gets \sum_{\{s,a,r,s'\} \in T} \nabla_\omega \lVert \hat{B}_\phi(s,a) - Q_\omega(s,a) \rVert^2_2 \)
            \State \(\omega \gets \omega - \eta_\omega \Delta_\omega\)
        \EndWhile
    \EndFunction
\end{algorithmic}
\end{algorithm}
